% moderncv

\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{banking}
\usepackage[utf8]{inputenc}
\usepackage[top=1cm, bottom=1.5cm, left=1.5cm, right=1.5cm]{geometry}

%custom head & body
\usepackage{moderncvheadcustom}
\usepackage{moderncvbodycustom}

% Largeur de la colonne pour les dates
\setlength{\hintscolumnwidth}{2.5cm}

\firstname{Max}
\familyname{Mattone}
\title{Software engineer (Mines-Télécom)}
\address{Dublin}{Ireland}
\email{mattone.m@gmail.com}
\url{https://mattonem.github.io/}
\mobile{+336 66 57 32 64}
\extrainfo{33 years old -- Driving licence}
\begin{document}
\maketitle


\section{Education}
\cventry{2011 -- 2014}{Master Engineering Degree}{Mines Douai -- French engineering school}{Douai}{France}{Specialisation in information and communication technology}
\cventry{2009 -- 2011}{B.Sc. Physics and Engineering}{Lycée Massena}{Nice}{France}{French Preparatory Classes to Top Schools (CPGE)}

\section{Work Experience}

\cventry{nov 2020 -- today}{Customer software engineer/Presale engineer}{Browserstack}{Dublin}{Ireland}{
Customer solutions engineer for the Browserstack testing platform for the Enterprise EMEA segment.
\begin{itemize}
\setlength{\itemindent}{0.25in}
\item Constantly stay ahead in communicating with customers.
\item Support the platform integration in the customer devlopment cycle. 
\item Present new features and products to customers, gather feedback and drive the adoption. 
\item Insure technical win on customer Proof of Concept. 
\end{itemize}
}

\cventry{july 2019 -- nov 2020}{Cloud technical lead engineer}{Orange, Sogeti contractor}{Sophia Antipolis}{France}{
Backend development for the Orange portail.
\begin{itemize}
\setlength{\itemindent}{0.25in}
\item PHP backends design, implementation and maintenance.
\item Reconciliation of multiple data sources using MySQL and Elastic Search databases.
\item Continuous integration and deployement in cloud using Gitlab and CloudFoundry.
\item Production monitoring with Kibana and Elastic Search.
\end{itemize}
}

\cventry{sept 2017 -- june 2019}{Software engineer consultant}{Amadeus, Sogeti contractor}{Sophia Antipolis}{France}{
Back end development mission as part of the hotel booking distribution business team.
\begin{itemize}
\setlength{\itemindent}{0.25in}
\item Scrum team in a SAFe organisation.
\item C++ backend development with MoM (Message-Oriented Middleware).
%\item Analysis and technical solutions design to fulfil client need in Agile methodology.
\item Incident analysis and maintenance of the solution components with continuous integration.
\item Studies and implementation of proof of concept to improve internal tooling.
\end{itemize}
}

\cventry{may 2016 -- sept 2017}{Software quality assurance engineer consultant}{Air-France, Sogeti contractor}{Sophia Antipolis}{France}{
QA engineering mission for Cascade project --- reengineering program of Air-France's flight planning system.
\begin{itemize}
\setlength{\itemindent}{0.25in}
\item Functional analysis of the client needs: planning of standard flight, broadcast adjustments, \ldots
\item Design and execution of manual and automatic test suite in Agile methodology.
\item Insure regression test suite quality.
\item Design and development of an in-house message injector (SOAP, SSM, ASM) for automated test suites. 
\end{itemize}
}

\cventry{oct 2015 -- nov 2015}{Software research engineer}{École des Mines Douai}{Douai}{France}{
Study and development of strategies for Wi-Fi coverage exploration and mapping.
This study is a follow-up to an original work in 2014 at Mines Douai trying to tackle the indoor geolocation challenge using domestic Wi-Fi coverage mapping. 
\begin{itemize}
\setlength{\itemindent}{0.25in}
	\item Architecture design for robotic intelligence.
    \item C++ development for coverage map management.
    \item Pharo (Smalltalk) development of exploration strategies definitions.
    \item Design of strategies for Wi-Fi mapping.
\end{itemize}
}

\cventry{nov 2014 -- oct 2015}{Software research engineer}{Inria Lille - Nord Europe \& École des Mines Douai}{Lille}{France}{
How to get full benefit of a live coding environment like Pharo when working in a highly distributed robotic system ?
\begin{itemize}
\setlength{\itemindent}{0.25in}
    \item Development of a prototype to broadcast dynamic update and migrations within Pharo platform.
    \item Design and implementation of a Bootstrap process for the Pharo platform.
    \item Contribution to open-source project PhaROS (ROS (Robotic Operating System) client for smalltalk).
    \item Contribution to open-source project Pharo.
    \item SLAM (Simultaneous Localization And Mapping) demonstration using Lidar (light detection and ranging) and robots like robuLAB et Kobuki.
\end{itemize}
}

\subsection{Trainings}

\cventry{april -- oct 2014}{Software engineer}{Inria Lille - Nord Europe}{Lille}{France}{
Study and implementation of an architecture agnostic JIT (Just In Time) compiler, as a trainee in RMoD team (Remodularization Object-oriented Development).
\begin{itemize}
\setlength{\itemindent}{0.25in}
\item Study and implementation of a multi-architecture compiler (mainly x86 \& ARM).
\item Contribution to open-source project Pharo.
\end{itemize}
}

\cventry{ march -- sept 2013}{Web engineer}{Dynaclic}{Bruxelles}{Belgium}{
Development of an ERP platform for schools, colleges and universities.
\begin{itemize}
\setlength{\itemindent}{0.25in}
\item MySQL database conception and maintenance.
\item Web PHP development with the Yii framework.
\end{itemize}
}

\cventry{may -- aug 2012}{Engineer assistant}{ESA (European Space Agency)}{Noordwijk}{Netherlands}{
Collaborated with inhabited flight control segment with the ERA (European Robotic Arm) project.
\begin{itemize}
\setlength{\itemindent}{0.25in}
\item Define and document network interfaces insuring secured communications to operate the robotic arm safely.
\item Design and implementation of a database to help project management.
\end{itemize}
}

\section{Other Experiences}

\cventry{oct 2016 -- jan 2021}{Lead engineer}{ARB-C (Association des Résidents Bétahon-Cromenach)}{}{France}{
Study, design, implementation, deployment and maintenance of a website for a local association of inhabitants in Brittany.
\begin{itemize}
\setlength{\itemindent}{0.25in}
\item Implementation of a blog using Seaside framework.
\item Host, deploy and maintain the solution using Docker.
\end{itemize}
}

\cventry{sept 2013 -- june 2014}{IT project lead engineer}{Ironmines (Coupe de France de Robotique)}{Douai}{France}{
École des Mines Douai's team to compete at the french robotic championship (Coupe de France de Robotique --- 28th to 31st of May 2014)
\begin{itemize}
\setlength{\itemindent}{0.25in}
\item Design and implementation of an autonomous robotic platform using the ROS middleware.
\item Implementation of plans and routines to achieve the different challenges during the competition.
\end{itemize}
}

\section{Languages}
\cvdoubleitem{French}{Native language}{English}{Fluent}

\section{IT skills}

\cvcomputer{OO Languages}{Smalltalk, Java, PHP, C++, CLOS, Python, Ruby}{Other Languages}{C, Bash, Pearl, Lisp, QML, ARM Assembly, Intel Assembly}
\cvcomputer{Reengineering}{Graph theory, Scientific visualisation, Moose}{Environnements}{Eclipse, Message-Oriented Middleware, Yii, Moose, \mbox{Jenkins}, J2EE}
\cvcomputer{Software architecture}{Cloud Foundry, AWS, ROS, Docker, Merise, UML, Design Patterns, Mind maps}{Project management}{Agile methodology, DevOps, SAFe, Scrum, \mbox{Kanban}, V cycle, TDD, ATDD, BDD}
\cvcomputer{Database}{MySQL, Oracle, Elastic Search, MongoDB}{Front}{HTML, CSS, JavaScript, Qt, Android, Vue.js}
\cvcomputer{Operating System}{Windows, macOS, Linux}{Versioning}{Git, svn, Mercurial}

\section{Interests}

\cvline{Sport}{Sailing (2 years of competition, Tall Ship Race 2014)}
\cvline{Hobbies}{Cinema, travel, theatre (4 year of conservatoire study, 13 performances in 2017), board games}
\cvline{Engineering}{Astronomy, robotics, mechanics, classic cars, electronics}

\nocite{*}
\bibliographystyle{apalike}
\bibliography{pub}



\end{document}
 
